\documentclass[11pt,letterpaper]{moderncv}

%-------------------------------------------------------------------------------
% CONFIGURATION
%-------------------------------------------------------------------------------
\moderncvstyle[nosymbols]{classic} % style options: casual, classic, banking, oldstyle
\moderncvcolor{orange}    % color options: blue, orange, green, red, purple, grey, black
\nopagenumbers{}        % suppress automatic page numbering

\usepackage[scale=0.75]{geometry} % adjust the page margins
\setlength{\hintscolumnwidth}{4cm} % adjust the width of the column with dates
\usepackage[T1]{fontenc}      % (A) 欧文フォントエンコーディング
\usepackage{lmodern}          % (A) Latin Modernフォント
\renewcommand{\familydefault}{\sfdefault} % (B) 全文書をSans Serifにする

%-------------------------------------------------------------------------------
% PERSONAL DATA
%-------------------------------------------------------------------------------
\renewcommand*{\addressfont}{\small\mdseries\raggedright}

\name{Rihito}{Arai}
\title{Senior Software Engineer}
\address{}{Nagano, Japan} % City, Country
\phone[mobile]{+81 (90) 7948-0077}
\email{licht.e.jima@gmail.com}
\social[linkedin]{rihito}
\social[github]{rhty}

\begin{document}

%-------------------------------------------------------------------------------
% NAME AND TITLE
%-------------------------------------------------------------------------------
\makecvtitle

%-------------------------------------------------------------------------------
% SUMMARY
%-------------------------------------------------------------------------------
\section{Professional Summary}
A hands-on \textbf{Senior Software Engineer and CTO} with \textbf{7+ years} of experience building backend platforms and AI-enabled products with \textbf{Go and TypeScript}.
Leads product architecture and delivery across LLM pipelines, backend services, cloud infrastructure, and internal tools.
Proven track record of designing multitenant access-control architectures, improving testing and release processes in legacy systems, and taking products from requirements to production.
Effective at bridging business and engineering teams in bilingual, cross-cultural environments, with professional experience in both Japan and Canada.

%-------------------------------------------------------------------------------
% AVAILABILITY
%-------------------------------------------------------------------------------
\section{Availability}
Available from August 2026 for fully remote engagements.
Seeking project-based full-time contracts of up to six months, or longer-term part-time work of approximately 25 hours per week.
Particularly interested in opportunities with English-speaking international teams.

%-------------------------------------------------------------------------------
% KEY SKILLS
%-------------------------------------------------------------------------------
\section{Key Skills}
\cvitem{Backend \& Languages}{Go, TypeScript (NestJS), Ruby, Python, Google Apps Script}
\cvitem{AI \& Data}{Multi-model LLM pipeline design, OpenAI / Anthropic / Google APIs, data warehouse pipelines, AI-assisted data operations}
\cvitem{Frontend}{React, Angular, shadcn/ui, MUI}
\cvitem{Infrastructure \& DevOps}{AWS, GCP (Cloud Run, GKE, Cloud SQL, Pub/Sub, Cloud Build, Firebase), Docker, Kubernetes, Terraform, GitHub Actions, GitLab CI/CD, Jenkins, Datadog, Sentry, Fastly, Cloudflare}
\cvitem{Databases}{PostgreSQL, MySQL, MSSQL, Redis, DynamoDB}
\cvitem{Architecture \& Security}{Microservices, multitenancy, ACL / RBAC, encryption and compliance for sensitive personal data}
\cvitem{APIs \& Integrations}{REST, OpenAPI / Swagger, gRPC, GraphQL, OAuth 2.0, Stripe, Ory Keto / Kratos}
\cvitem{Quality \& Leadership}{Technical leadership, CI/CD, legacy refactoring, test strategy, code review, Scrum Master}
\cvitem{Languages}{Japanese (Native), English (Business; 3+ years of professional experience), Spanish (Beginner)}

%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------
\section{Work Experience}
% -- VisionCompass
\cventry
    {Apr 2026 -- Present}
    {CTO}
    {VisionCompass Inc.}
    {Japan (Remote)}
    {}
    {
      \begin{itemize}
        \item Lead backend, infrastructure, AI, and admin-platform development for \textbf{Neruzo}, an AI-powered journaling and sleep application launched on July 13, 2026.
        \item Architected and implemented a flexible, graph-based LLM pipeline with configurable nodes and conditional branching across OpenAI, Anthropic, and Google models to summarize journals, analyze conversations, and organize users' thought patterns.
        \item Built a Dockerized Go backend on GCP Cloud Run with Supabase, plus a React and shadcn/ui administration platform.
        \item Implemented database-backed asynchronous processing with polling Cloud Run workers and concurrent execution to use LLM API wait time efficiently.
      \end{itemize}
    }

% -- COTEN
\cventry
    {Aug 2025 -- Jul 2026}
    {Software Engineer (Contract)}
    {COTEN Inc.}
    {Japan (Remote)}
    {}
    {
      \begin{itemize}
        \item Designed and implemented AI-powered Google Sheets tooling in TypeScript and Google Apps Script, automating world-history data curation tasks that were impractical to perform manually.
        \item Led the design and implementation of multitenancy, organization models, and ACLs for a data-warehouse-as-a-service platform.
        \item Designed and implemented data pipelines and backend APIs using TypeScript and NestJS.
        \item Managed a Bangladesh-based engineering team and collaborated on the technical design of a React administration UI migration from MUI to shadcn/ui.
      \end{itemize}
    }

% -- CIBC
\cventry
    {Jan 2025 -- Oct 2025}
    {Senior Applications Developer}
    {CIBC (Canadian Imperial Bank of Commerce)}
    {Toronto, Canada (Hybrid)}
    {}
    {
      \begin{itemize}
        \item Developed and stabilized an internal corporate-security case-management and assessment platform using Go, TypeScript / Angular, MSSQL, and Windows Server.
        \item Gained stakeholder support to include refactoring and automated testing in the delivery plan, helping the team achieve stable releases with few observed errors.
        \item Improved Jenkins pipelines and standardized the release workflow, reducing friction and risk during deployments.
        \item Proposed and implemented internal API improvements, including new schemas and reverse-proxy integration between legacy and new systems; also identified security and data-consistency issues.
        \item Contributed to a delivery recognized by department leadership as its most successful project, while mentoring junior engineers through backend and CI/CD knowledge-sharing sessions.
      \end{itemize}
    }

% -- WealthPark
\cventry
    {Nov 2021 -- Feb 2025}
    {Senior Software Engineer / (Acting) Tech Lead}
    {WealthPark Co., Ltd.}
    {Tokyo, Japan (Remote)}
    {}
    {
      \begin{itemize}
        \item Built a Go (go-kit) access-control microservice on AWS EKS with Ory Keto and developed Python / Airflow / AWS Lambda pipelines for external real estate data.
        \item \textbf{Alternative Investment Project (Apr 2022 -- Feb 2025)}:
        \begin{itemize}
          \item Joined at inception, clarified ambiguous requirements, and implemented investor registration and fund management features with Go microservices and gRPC.
          \item Led four engineers and introduced unit testing and code review practices, raising overall coverage from $30\%$ to $\sim70\%$ and new-feature coverage to $\sim90\%$.
          \item Dealt with MyNumber data (similar to SIN), ensuring encryption and compliance with government regulations.
          \item Operated in an English-speaking environment, bridging communications between global dev teams and Japanese stakeholders.
        \end{itemize}
      \end{itemize}
    }

% -- WED
\cventry
    {Jun 2019 -- Oct 2021}
    {Server-Side and Research Engineer / Scrum Master}
    {WED, inc.}
    {Tokyo}
    {}
    {
      \begin{itemize}
        \item Built and maintained backend services in Go, Ruby on Rails, Python on GCP.
        \item Resolved critical concurrency issues in a high-traffic money management service ($\sim100\mathrm{K}$ MAU), preventing data inconsistency before it impacted end users.
        \item Served as Scrum Master, introducing agile ceremonies, code review guidelines, and linting tools to reduce bottlenecks and enhance team autonomy.
      \end{itemize}
    }

% -- FiNC
\cventry
    {Oct 2018 -- Jun 2019}
    {Intern Server-Side Engineer}
    {FiNC Technologies, Inc.}
    {Tokyo, Japan}
    {}
    {
      \begin{itemize}
        \item Developed REST APIs with Ruby on Rails for health/fitness mobile apps.
        \item Integrated OAuth2.0-based social logins (LINE, Facebook).
        \item Gained foundational skills in microservice design, DB architecture, and user authentication.
      \end{itemize}
    }

% -- Freelance
\cventry
    {Feb 2020 -- Present}
    {Freelance / Side Projects}
    {}
    {}
    {}
    {
      \begin{itemize}
        \item \textbf{Enterprise LLM Pipeline and Admin Tooling (TypeScript, Ruby on Rails, Google Apps Script)}:
        Collaborated with a startup client to improve internal LLM workflows and develop custom admin tooling.
        Enhanced pipeline reliability and developer UX by organizing legacy scripts and adding new UI components.
        \item \textbf{Meditation App Backend (Ruby on Rails, GCP)}:
        Single-handedly built user management and audio content features; deployed via Terraform on GCP.
      \end{itemize}
    }

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------
\section{Education}

\cventry
    {Sep 2021}
    {M.Eng. in Electrical Engineering \& Information Systems}
    {The University of Tokyo}
    {Tokyo, Japan}
    {}
    {
      \begin{itemize}
        \item Researched entity matching algorithms for receipts (Python, ML).
      \end{itemize}
    }

\cventry
    {Mar 2017}
    {B.Eng. in Applied Physics}
    {Hokkaido University}
    {Hokkaido, Japan}
    {}
    {
      \begin{itemize}
        \item Studied complex network theory and computational methods (Fortran).
      \end{itemize}
    }

\end{document}
